%-------------------------
% Resume in LateX
% Author : Le Hong Son
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{}{\Large Le Hong Son}} & Email: \href{mailto:Lsonofficial09@gmail.com}{Lsonofficial09@gmail.com}\\
  \href{https://github.com/lesondowski}{Github: Lesondowski} & Mobile/Zalo: \href{}{0585 252 743} \\
\end{tabular*}


\section{Summary}
        { I'm looking for a stable role that aligns with my expertise and allows me to effectively contribute to the company's objectives through data driven solutions. I'm eager to utilize my analytical skills and problem solving abilities to support the organization in achieving its goals.}
        


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Saigon University}{Ho Chi Minh}
      {Major Computer Science;}{9 / 2021 -- Now}
    \resumeSubheading
      {Certificate}{}
      {Google Data Analytics Professional Certificate}{8 / 2024}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Sendo}{Ho Chi Minh}
      {Data Analytics Intern }{5 / 2024 -- 8 / 2024}
      \resumeItemListStart
        \resumeItem{Description}
          {Worked with the Quality Assurance (QA) department, processing raw data on delivery quality and order-related complaints. Utilized visual tools to monitor real-time data. Developed automatically updated daily reports}
        \resumeItem{Technology}{Python (Numpy, Pandas), Power BI, Excel}
        \resumeItem{Responsibility}{}
        
          {Processed raw data for the SQA department. Preprocessed and cleaned raw data provided by the QA department, formatting fields and columns while performing preliminary calculations on datasets ranging from 500MB to 800MB.}
          
          {Delivered clean and structured datasets that were used for visualization in Power BI. Additionally, conducted statistical analysis, including counting defects and samples in quality control testing for products.}
      \resumeItemListEnd

\resumeSubHeadingListEnd
%-----------Technical Skill-----------------
\section{Technical Skill}
\resumeSubHeadingListStart
    \resumeSubItem{Programming Language }{Python}
    
    \vspace*{0.2cm}{Packages : Numpy, Pandas, Matplotlib, Seaborn, sklearn }{}
   \resumeSubItem {Database Management System}{Mysql, Sql Server Management}
    \resumeSubItem{Visualization Tools}{Power BI, Excel, Looker Studio, Tableau}
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------

\section{Projects}
\resumeSubHeadingListStart
    \resumeSubItem{\href{https://lookerstudio.google.com/u/1/reporting/361a7bd0-eb84-4edc-a199-d421fd95e858/page/p_hurf7mq9jd}{Revenue Growth Strategy for Clients}}
    {}
    
    \vspace*{0.27cm}{Increased revenue from VND 10 billion to VND 20 billion in one month. Analyzed key performance indicators (KPIs) to identify significant insights from data and provided actionable recommendations.}
    
    \vspace*{-0.1cm}{Managed and filtered data using Excel. Visualized data with Looker Studio by creating charts to compare key metrics.}
    
    \vspace*{-0.1cm}{Delivered conclusions and insights from the data, and recommended strategies to enhance revenue growth.}
 \resumeSubItem{\href{https://github.com/lesondowski/Predictive-Customer-Analytics}{Other Projects}}
 
   \vspace*{0.27cm}{Predictive Customer Analytics (Python, Excel, Data Visualization)}

   {Salifort Motors (Looker Studio, Data Visualization)}
\resumeSubHeadingListEnd


\section{Long-term Goals}
        {Secure a stable job after graduation. Enhance skills, experience, and knowledge. Acquire practical knowledge and delve deeper into the professional field}
        
\section{Short-term Goal}
        {Aspiring to secure a stable job that aligns with my expertise. Engaging in practical projects to gain both experience and knowledge.Continuously learning and enhancing skills outside the classroom before graduation.}


%-------------------------------------------
\end{document}
